A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\script{FitComparison_3panelPlot.py}
\includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
The top panel shows the full two dimensional \SFRDzZ linear in time. The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$. We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in each panel with grey dotted lines. For the latter, the contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our newly defined functional form of \SFRDzZ as defined in the previous section to the Illustris-TNG cosmological simulations. Below we briefly summarise relevant physics behind the Illustris-TNG simulations, and we elaborate on our choices made during the fitting procedure.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Effect on the local mass distribution of BBH mergers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq. \ref{eq: z log skew}).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
The top panel shows the full two dimensional \SFRDzZ linear in time. The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$. We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in each panel with grey dotted lines. For the latter, the contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our newly defined functional form of \SFRDzZ as defined in the previous section to the Illustris-TNG cosmological simulations. Below we briefly summarise relevant physics behind the Illustris-TNG simulations, and we elaborate on our choices made during the fitting procedure.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application: systematic variations of \SFRDzZ and the effect on the mass distribution of merging BBHs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers.
To this end we use the publicly available simulations as presented in \cite{vanson+2022}
We use the framework described in detail in \cite{vanson+2022} that is part of the \COMPAS suite to compute local merger rates of BBH systems originating from

% We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq. \ref{eq: z log skew}).

% We study merging binary black holes formed from the
% evolution of isolated massive binary stars (the ‘isolated
% binary evolution’ channel) using the publicly available
% simulations presented in Broekgaarden et al. (2021);
% Broekgaarden et al. (2022). These simulations were per-
% formed using the rapid binary population synthesis suite
% COMPAS4 (Stevenson et al. 2017; Vigna-G ́omez et al.
% 2018; Broekgaarden et al. 2019; Team COMPAS: Riley
% et al. 2022), which employs simple parameterized models
% of single (Hurley et al. 2000) and binary stellar evolu-
% tion (Hurley et al. 2002) in order to rapidly evolve large
% populations of binaries.
